{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-16 bmvc_review.tex
Table Colors Added

We also compare the proposed {\it E}nKCF tracker to the LCT \cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}. 
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$,  $R_{s}$) in  {\it E}nKCF, we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ with similar
run-time performance. On the other hand, we employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as we run filters in every frame. Running another filter, 
$R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
tracker ({\it m}LCT) and run $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given order. $R_{t}^{S}$ uses the translation estimation given by $R_{t}^{L}$ to update
translation and $R_{s}$ uses the final translation estimation given by $R_{t}^{S}$ to update scale. Interestingly, running two complementary translation filter results in significant improvement
at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
high speed but also more accurate tracker than the baseline methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & 53.9 & 48.93 &52.41 & 48.10 & \color{red} 55.85 & 52.14 & \textbf{58.16} \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 39.89 & 38.51 & \textbf{41.58} \\
FPS & \color{red} 416 & 412 & 370 & \textbf{425}  & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run the filters in every frame in the listed order. The LCT tracker \cite{ma2015long} runs a translation and scale filter in every frame (similar to $6^{th}$ method) and couples a re-detection method to perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

>>>>

We also compare the proposed {\it E}nKCF tracker to the LCT \cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}. 
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$,  $R_{s}$) in  {\it E}nKCF, we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ with similar
run-time performance. On the other hand, we employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as we run filters in every frame. Running another filter, 
$R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
tracker ({\it m}LCT) and run $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given order. $R_{t}^{S}$ uses the translation estimation given by $R_{t}^{L}$ to update
translation and $R_{s}$ uses the final translation estimation given by $R_{t}^{S}$ to update scale. Interestingly, running two complementary translation filter results in significant improvement
at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
high speed but also more accurate tracker than the baseline methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425  & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run the filters in every frame in the listed order. The LCT tracker \cite{ma2015long} runs a translation and scale filter in every frame (similar to $6^{th}$ method) and couples a re-detection method to perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}
